Dm Deamination Sequence and Position Figure Generation

### 2022-06-14 R/DrosophilaDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update Drosophila notebooks
- Support for all_reps
- Read length counting occurs during data generation

expansionOffset = 10
cellType = "Dm"
CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
minReadLength = 23; maxReadLength = 32

>>>>

expansionOffset = 10
cellType = "Dm"
CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 23; maxReadLength = 32

### 2022-06-14 R/DrosophilaDeaminationSequenceAndPositionFigureGeneration.rmd
Update Drosophila notebooks
- Support for all_reps
- Read length counting occurs during data generation

cellType = "Dm"
CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
minReadLength = 23; maxReadLength = 32

>>>>

cellType = "Dm"
CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 23; maxReadLength = 32
